---
title: Shiny + R Markdown = interactive documents
output: html_document
runtime: shiny
---

This R Markdown document is made interactive using Shiny. This is similar to Shiny apps only you don't need a ui.R file - R Markdown handles the formatting for you. You just need to define inputs and outputs. Colleagues can be emailed the `.Rmd` file and run them locally by clicking "Run Document".

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).


### Here are two Shiny widgets

```{r eruptions, echo=FALSE}
selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20)
  
sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
```

### that create a reactive plot

```{r echo = FALSE}
renderPlot({
  hist(faithful$eruptions, probability = TRUE, 
       breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", 
       main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```
